Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-01-28 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
correction of code, No planting date in NGA trials were giving NAs

Goolhi_13_dat <- cbind(Goolhi_13_dat,
                          AUDPC = apply(data.frame(zero = 1,
                                                   Goolhi_13[,c("Inc_16D","Inc_33D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c((Goolhi_13_dat$first_sign_disease[1]-7)-
                                                     Goolhi_13_dat$planting_date[1],
                                                  16,33)
                                        )
                          )

@@

Goolhi_13_m <- Goolhi_13_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, 
            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = sum(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = Goolhi_13_dat[Goolhi_13_dat$fungicide_ai == "propiconazole" | 
                                                        Goolhi_13_dat$fungicide_ai == "control" ,]))[1,3]
   )

#!!!!!!!!!!!!!!!!!! Check to see if errors are calculated
Goolhi_13_m <- fold_data(Goolhi_13_m, PM_MB_means)

@@

MarysM_13_dat <- cbind(MarysM_13_dat,
                          AUDPC = apply(data.frame(zero = 1,
                                                   MarysM_13[,c("Inc_18D","Inc_19D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c((MarysM_13_dat$first_sign_disease[1]-7)-
                                                     MarysM_13_dat$planting_date[1],
                                                  12,12+19)
                                        )
                          )
```

#### Calculating the treatment means
```{r Marys_means}
MarysM_13_m <- MarysM_13_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, 
            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = length(as.numeric(replicate)),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = MarysM_13_dat[MarysM_13_dat$fungicide_ai == "propiconazole" | 
                                                        MarysM_13_dat$fungicide_ai == "control" ,]))[1,3]

>>>>

Goolhi_13_dat <- cbind(Goolhi_13_dat,
                          AUDPC = apply(data.frame(zero = 1,
                                                   Goolhi_13[,c("Inc_16D","Inc_33D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c(1,
                                                  16,33)
                                        )
                          )

@@

Goolhi_13_m <- Goolhi_13_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, 
            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = length(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              #disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              #yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = Goolhi_13_dat[Goolhi_13_dat$fungicide_ai == "propiconazole" | 
                                                        Goolhi_13_dat$fungicide_ai == "control" ,]))[1,3]
   )

# For some wierd reason standard deviations are comming back NA in the code above
# Because of n_treatment being converted to a factor I need to wrangle carefully here
Goolhi_tmp <- Goolhi_13_dat %>%
   group_by(n_treatment) %>%
   summarise(#PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             disease_error = sd(PM_final_severity, na.rm = TRUE),
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE))

Goolhi_13_m <- left_join(Goolhi_13_m, Goolhi_tmp)

Goolhi_13_m <- fold_data(Goolhi_13_m, PM_MB_means)

@@

MarysM_13_dat <- cbind(MarysM_13_dat,
                          AUDPC = apply(data.frame(zero = 1,
                                                   MarysM_13[,c("Inc_18D","Inc_19D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c(1,12,12+19)
                                        )
                          )
```

#### Calculating the treatment means
```{r Marys_means}
MarysM_13_m <- MarysM_13_dat %>%
   group_by(n_treatment) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             host_genotype = unique(host_genotype),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             fungicide_ai = unique(fungicide_ai),
             dose_ai.ha = unique(dose_ai.ha),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = length(as.numeric(replicate)),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = MarysM_13_dat[MarysM_13_dat$fungicide_ai == "propiconazole" | 
                                                        MarysM_13_dat$fungicide_ai == "control" ,]))[1,3]
